\textbf{ Interpretable Gaussian Processes for Stellar Light Curves }

### 2020-07-30 tex/ms.tex
coded up second moment

        \parbox[t]{\linewidth}{$l = l',               \\m = m' = 0$}

@@

        {2 \sqrt{2l' + 1} (1 + c r)^{l' + 1}}
        \parbox[t]{\linewidth}{\vspace{-3em}$l = 0,   \\l' > 0, \\m = m' = 0$}

@@

@@

        \parbox[t]{\linewidth}{\vspace{-4.75em}$l = l', \\m = m' = 0$}

@@

        \textrm{same as previous case, but with $l \rightarrow l'$}
        \parbox[t]{\linewidth}{\vspace{-2em}$l = 0,     \\l' > 0, \\m = m' = 0$}

@@

            (\alpha +\beta +1) \sqrt{(2 l+1) (2 p+1)}}

@@

The final step is to evaluate the integral in Equation~(\ref{eq:Er2}), given
the PDF in Equation~(\ref{eq:lognormal}):
%
\begin{align}
    \mathrm{E} \big[ y_{lm} y_{l'm'} \big]
     & =
    \begin{dcases}
        1 + \frac{\left(\alpha +1\right) \alpha
            \gamma_2 c^2}{4 \left(c+1\right)
            \left(\alpha + \beta \right)}
        \\[0.75em]
        \quad\quad\quad\quad\quad
        -\frac{\alpha  \gamma_1 c}{\alpha +\beta }
        \\[0.75em]
        \quad\quad\quad\quad\quad
        \times
        \bigg[G_0^1
            +
            \frac{\left(\alpha +1\right) \gamma_2
                c \left(\alpha +\beta +\alpha  c+c\right)}{4 \gamma_1 \left(c+1\right)
                \left(\alpha +\beta +1\right)} G_0^2\bigg]
         &
        \quad\quad
        \parbox[t]{\linewidth}{\vspace{-4.75em}$l = l', \\m = m' = 0$}
        \\[2em]
        %
        -\frac{\alpha \gamma_1 c}{2 \sqrt{2 l+1} (\alpha +\beta )}
        \\[0.75em]
        \quad\quad\quad\quad\quad
        \times
        \bigg[
            2G_l^1
            + \dfrac{c(\alpha + 1)}{\alpha + \beta + 1} G_l^2
            \\[0.75em]
        \qquad
        -\dfrac{c\gamma_2(\alpha + 1)}{\gamma_1(\alpha + \beta + 1)} G_{l+1}^2
        \\[0.75em]
        \qquad
        -\dfrac{c^2\gamma_2(\alpha + 1)(\alpha + 2)}{2\gamma_1(\alpha + \beta + 1)(\alpha + \beta + 2)} G_{l+1}^3
        \bigg]
         &
        \quad\quad
        \parbox[t]{\linewidth}{\vspace{-7.5em}$l > 0,   \\l' = 0, \\m = m' = 0$}
        \\[2em]
        %
        \textrm{same as previous case, but with $l \rightarrow l'$}
         &
        \quad\quad
        \parbox[t]{\linewidth}{\vspace{-2em}$l = 0,     \\l' > 0, \\m = m' = 0$}
        \\[2em]
        %
        \frac{\alpha  (\alpha +1) \gamma_2 c^2}{(\alpha +\beta )
            (\alpha +\beta +1) \sqrt{(2 l+1) (2 p+1)}}
        \\[0.75em]
        \quad\quad\quad\quad\quad
        \times
        \bigg[
        G_{l+l'+1}^2
        +
        \frac{c(\alpha + 2)}{\alpha + \beta + 2}G_{l+l'+1}^3
        \\[0.75em]
        \qquad
        +
        \frac{c^2(\alpha + 2)(\alpha + 3)}{4(\alpha + \beta + 2)(\alpha + \beta + 3)}G_{l+l'+1}^4
        \bigg]
         &
        \quad\quad
        \parbox[t]{\linewidth}{\vspace{-5.25em}$l > 0,  \\l' > 0, \\m = m' = 0$}
        \\[2em]
        %
        0
         &
        \quad\quad m, m' \ne 0
        \quad,
    \end{dcases}
\end{align}
%
where we define
%
\begin{align}
    \gamma_2 \equiv 1
    - 2\exp\bigg[ \mu + \frac{1}{2}\nu\bigg]
    + \exp\bigg[ 2\mu + 2\nu\bigg]
    \quad.
\end{align}

>>>>

        \parbox[t]{\linewidth}{$l = l' = 0,           \\m = m' = 0$}

@@

@@

where, by symmetry, the expression for $l' > 0, \, l = 0, \, m = m' = 0$ is the same as
in the second case, provided we make the substitution $l \rightarrow l'$.

@@

        \parbox[t]{\linewidth}{\vspace{-4.75em}$l = l' = 0, \\m = m' = 0$}

@@

@@

            (\alpha +\beta +1) \sqrt{(2 l+1) (2 l'+1)}}

@@

The final step is to evaluate the integral in Equation~(\ref{eq:Er2}), given
the PDF in Equation~(\ref{eq:lognormal}):
%
\begin{align}
    \mathrm{E} \big[ y_{lm} y_{l'm'} \big]
     & =
    \begin{dcases}
        1 + \frac{\left(\alpha +1\right) \alpha
            \gamma_2 c^2}{4 \left(c+1\right)
            \left(\alpha + \beta \right)}
        \\[0.75em]
        \quad\quad\quad\quad\quad
        -\frac{\alpha  \gamma_1 c}{\alpha +\beta }
        \\[0.75em]
        \quad\quad\quad\quad\quad
        \times
        \bigg[G_0^1
            +
            \frac{\left(\alpha +1\right) \gamma_2
                c \left(\alpha +\beta +\alpha  c+c\right)}{4 \gamma_1 \left(c+1\right)
                \left(\alpha +\beta +1\right)} G_0^2\bigg]
         &
        \quad\quad
        \parbox[t]{\linewidth}{\vspace{-4.75em}$l = l' = 0, \\m = m' = 0$}
        \\[2em]
        %
        -\frac{\alpha \gamma_1 c}{2 \sqrt{2 l+1} (\alpha +\beta )}
        \\[0.75em]
        \quad\quad\quad\quad\quad
        \times
        \bigg[
            2G_l^1
            + \dfrac{c(\alpha + 1)}{\alpha + \beta + 1} G_l^2
            \\[0.75em]
        \qquad
        -\dfrac{c\gamma_2(\alpha + 1)}{\gamma_1(\alpha + \beta + 1)} G_{l+1}^2
        \\[0.75em]
        \qquad
        -\dfrac{c^2\gamma_2(\alpha + 1)(\alpha + 2)}{2\gamma_1(\alpha + \beta + 1)(\alpha + \beta + 2)} G_{l+1}^3
        \bigg]
         &
        \quad\quad
        \parbox[t]{\linewidth}{\vspace{-7.5em}$l > 0,       \\l' = 0, \\m = m' = 0$}
        \\[2em]
        %
        \frac{\alpha  (\alpha +1) \gamma_2 c^2}{(\alpha +\beta )
            (\alpha +\beta +1) \sqrt{(2 l+1) (2 l'+1)}}
        \\[0.75em]
        \quad\quad\quad\quad\quad
        \times
        \bigg[
        G_{l+l'+1}^2
        +
        \frac{c(\alpha + 2)}{\alpha + \beta + 2}G_{l+l'+1}^3
        \\[0.75em]
        \qquad
        +
        \frac{c^2(\alpha + 2)(\alpha + 3)}{4(\alpha + \beta + 2)(\alpha + \beta + 3)}G_{l+l'+1}^4
        \bigg]
         &
        \quad\quad
        \parbox[t]{\linewidth}{\vspace{-5.25em}$l > 0,      \\l' > 0, \\m = m' = 0$}
        \\[2em]
        %
        0
         &
        \quad\quad m, m' \ne 0
        \quad,
    \end{dcases}
\end{align}
%
where we define
%
\begin{align}
    \gamma_2 \equiv 1
    - 2\exp\bigg[ \mu + \frac{1}{2}\nu\bigg]
    + \exp\bigg[ 2\mu + 2\nu\bigg]
    \quad,
\end{align}
%
and the expression for $l' > 0, \, l = 0, \, m = m' = 0$ is again the same as in
the second case, provided we make the substitution $l \rightarrow l'$.
